---
title: "Phase 3 tracker"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard); library(RisePhaseIIILibrary); library(tidyverse); library(googlesheets4); library(yaml)
creds <- yaml::read_yaml("creds.yaml")

```

```{r setupdata}

googlesheets4::gs4_auth(email = creds$email)
tracker_data_raw <- read_sheet(ss = creds$tracker$url, sheet = creds$tracker$tracking_sheet, skip = 1, col_types = "cnccccnlllllllnlllc") 

tracker_data <- tracker_data_raw %>% 
  filter(!is.na(Name)) %>% 
  select(`1. Consent`:`7. Feedback`)

review_data <- read_sheet(ss = creds$interview_sheet$url, sheet = creds$interview_sheet$responses_sheet, col_types = "cccccccccccccccccccccc") %>% 
  select(`Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, `Interviewer Name (you, the interviewer)`, Intelligence:Boost) %>% 
  gather(Trait, Rating, -`Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, -`Interviewer Name (you, the interviewer)`) %>% 
  mutate(score = as.numeric(readr::parse_number(Rating)),
         score = ifelse(score == -9, NA, score)) %>% 
  group_by(Trait) %>% 
  mutate(score = score - mean(score, na.rm =T)) %>% 
  ungroup


teacher_ratings <- read_sheet(creds$teacher_interviews$url, sheet = creds$teacher_interviews$group_1, col_types = "ccnnnnnnnnnc")

for(s in creds$teacher_interviews[3:length(creds$teacher_interviews)]) {
  teacher_ratings <- bind_rows(teacher_ratings,
                               read_sheet(creds$teacher_interviews$url, sheet = s, col_types = "ccnnnnnnnnnc"))
}

teacher_ratings_long <- teacher_ratings %>%   
  select(Student:`Interview-ability`) %>%
  gather(Trait, `Teacher Score`, -Student:-`Student ID`) %>% 
  filter(!is.na(`Student ID`)) %>% 
  rename(Candidate = `Student ID`) %>% 
  group_by(Trait) %>% 
  mutate(`Teacher Score` = scale(`Teacher Score`)) %>% 
  ungroup

peer_nominations <- read_sheet(creds$peer_nominations$url, creds$peer_nominations$group_1) %>%
  mutate(`Student ID` = as.character(`Student ID`))

for(s in creds$peer_nominations[3:length(creds$peer_nominations)]) {
  peer_nominations <- bind_rows(peer_nominations,
                                read_sheet(creds$peer_nominations$url, sheet = s))
}

noms <- peer_nominations %>% 
  select(contains("classmate")) %>% 
  gather(nomination, Name) %>% 
  mutate(score = readr::parse_number(nomination),
         nomination = gsub(" [0-9]", "", nomination)) %>% 
  group_by(Name, nomination) %>% 
  tally() %>% 
  left_join(tracker_data_raw %>% select(Name, `Student ID`), by = "Name") %>% 
  mutate(Trait = case_when(nomination == "Boostable classmate" ~ "Boost",
                           nomination == "Intelligent classmate" ~ "Intelligence",
                           nomination == "Persevering classmate" ~ "Perseverance",
                           nomination == "High integrity classmate" ~ "Integrity",
                           nomination == "Empathetic classmate" ~ "Empathy",
                           TRUE ~ "Spike")) %>% 
  rename(Candidate = `Student ID`)


```

Pipeline {.storyboard}
====


### Student Pipeline

```{r}
tracker_data %>% 
  gather(Step, Completed) %>% 
  group_by(Step) %>% 
  summarise(`Number completed` = sum(Completed)) %>% 
  ggplot(aes(x = Step, y = `Number completed`)) +
  geom_bar(stat = "identity", fill = "blue", alpha = 0.6) +
  ggthemes::theme_hc() +
  theme(axis.text.x = element_text(angle = 270))
```


### Teacher pipeline

```{r}

```


Intelligence {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Intelligence"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr) ) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```

Perseverance {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Perseverance"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  theme(axis.text.y= element_blank()) +
  facet_grid(~`Evidence Type`) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```


Empathy {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Empathy"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```

Integrity {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Integrity"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```

Spike {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Spike"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```


Boost {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Boost"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```
