---
title: "Phase 3 tracker"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard); library(RisePhaseIIILibrary); library(tidyverse); library(googlesheets4); library(yaml)
creds <- yaml::read_yaml("creds.yaml")

```

```{r setupdata}

googlesheets4::gs4_auth(email = creds$email)

tracker_data_raw <- read_sheet(ss = creds$tracker$url, sheet = creds$tracker$tracking_sheet, skip = 1, col_types = "cnccccnlllllllnlllc") %>% 
  mutate(`Student ID` = tolower(`Student ID`))

tracker_data <- tracker_data_raw %>% 
  filter(!is.na(Name)) %>% 
  select(`1. Consent`:`7. Feedback`)

rmet_responses <- read_sheet(ss = creds$rmet$url, sheet = creds$rmet$responses_sheet) 
rmet_answers <- read_sheet(ss = creds$rmet$url, sheet = creds$rmet$answers) 

rmet_answers <- rmet_answers %>% 
  mutate(question_number = 1:n())

rmet_responses_long <- rmet_responses %>% 
  gather(Question, Answer, -1:-3) %>% 
  mutate(question_number = as.numeric(str_extract(Question, "[0-9]{1,2}")) - 3) %>% 
  left_join(rmet_answers, by = "question_number") %>% 
  group_by(`What is your name? (First then last)`) %>% 
  filter(Timestamp == min(Timestamp)) %>% 
  summarize(`Student ID` = first(`What is your student ID? (This is a unique numeric ID  associated with you at your school; if you do not have one, use the email with which we have corresponded with you.)`),
            score = sum(Answer == `Correct Answer`)) %>% 
  ungroup %>% 
  mutate(Percentile = ntile(score, 100), 
         `Student ID` = tolower(`Student ID`))


interview_data <- read_sheet(ss = creds$interview_sheet$url, sheet = creds$interview_sheet$responses_sheet, col_types = "cccccccccccccccccccccc") %>% 
  select(`Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, `Interviewer Name (you, the interviewer)`, Intelligence:Boost) %>% 
  gather(Trait, Rating, -`Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, -`Interviewer Name (you, the interviewer)`) %>% 
  rename(`Student ID` = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`,
         Interviewer = `Interviewer Name (you, the interviewer)`) %>%
  mutate(`Interview Score` = as.numeric(readr::parse_number(Rating)),
         `Interview Score` = ifelse(`Interview Score` == -9, NA, `Interview Score`),
         `Student ID` = tolower(`Student ID`)) %>%
  ungroup %>% 
  select(Interviewer, `Student ID`, Trait, `Interview Score`) %>% 
  left_join(tracker_data_raw %>% select(`Student ID`, Name), by = "Student ID")

teacher_ratings <- read_sheet(creds$teacher_interviews$url, sheet = creds$teacher_interviews$group_1, col_types = "ccnnnnnnnnnc") %>% 
  mutate(group = creds$teacher_interviews$group_1)

for(s in creds$teacher_interviews[3:length(creds$teacher_interviews)]) {
  teacher_ratings <- bind_rows(teacher_ratings,
                               read_sheet(creds$teacher_interviews$url, sheet = s, col_types = "ccnnnnnnnnnc") %>% 
  mutate(group = s))
}

teacher_ratings <- teacher_ratings %>% 
  mutate(`Student ID` = tolower(`Student ID`))

teacher_ratings_long <- teacher_ratings %>%   
  select(Student:`Interview-ability`, group) %>%
  gather(Trait, `Teacher Score`, -Student:-`Student ID`, -group) %>% 
  group_by(Trait, group) %>% 
  mutate(`Teacher Score` = scale(`Teacher Score`)) %>% 
  ungroup %>% 
  group_by(Student) %>% 
  mutate(Interviewability = `Teacher Score`[Trait == "Interview-ability"], 
         Creativity = `Teacher Score`[Trait == "Creativity"]) %>% 
  rename(Name = Student)


peer_nominations <- read_sheet(creds$peer_nominations$url, creds$peer_nominations$group_1) %>%
  mutate(`Student ID` = as.character(`Student ID`), 
         group_peer = creds$peer_nominations$group_1)

for(s in creds$peer_nominations[3:length(creds$peer_nominations)]) {
  peer_nominations <- bind_rows(peer_nominations,
                                read_sheet(creds$peer_nominations$url, sheet = s)%>% 
    mutate(group_peer = s)) 
}

peer_nominations <- peer_nominations %>% 
  mutate(`Student ID` = tolower(`Student ID`))

self_ratings <- peer_nominations %>% 
  select(`Student ID`, `Where would you place yourself in terms of intelligence?`:`Where would you place yourself relative to your peers in terms of need? If given more resources, how much more likely would you be to accomplish your dreams?`, group_peer)

self_ratings_long <- self_ratings %>% 
  rename(Intelligence = `Where would you place yourself in terms of intelligence?`, 
         Integrity = `Where would you place yourself in terms of integrity?`, 
         Perseverance = `Where would you place yourself in terms of perseverance?`, 
         Empathy = `Where would you place yourself in terms of empathy?`, 
         Spike = `Where would you place yourself relative to your peers in terms of how driven and passionate you are? How likely are you to dream a project and implement it?`, 
         Boost = `Where would you place yourself relative to your peers in terms of need? If given more resources, how much more likely would you be to accomplish your dreams?`) %>% 
  gather(Trait, Response, -group_peer, -`Student ID`) %>% 
  mutate(Score = parse_number(Response),
         `Student ID` = tolower(`Student ID`)) %>% 
  group_by(group_peer, Trait) %>% 
  mutate(scaled_score = scale(Score)) %>% 
  left_join(tracker_data_raw %>% select(Name, `Student ID`) %>% 
              mutate(`Student ID` = tolower(`Student ID`)), by = "Student ID") 

peer_noms_raw <- peer_nominations %>% 
  select(contains("classmate"), group_peer) %>% 
  gather(nomination, Name, -group_peer) %>% 
  mutate(nomination_number = readr::parse_number(nomination),
         nomination = gsub(" [0-9]", "", nomination)) %>% 
  mutate(Trait = case_when(nomination == "Boostable classmate" ~ "Boost",
                           nomination == "Intelligent classmate" ~ "Intelligence",
                           nomination == "Persevering classmate" ~ "Perseverance",
                           nomination == "High integrity classmate" ~ "Integrity",
                           nomination == "Empathetic classmate" ~ "Empathy",
                           TRUE ~ "Spike")) %>% 
  select(-nomination) %>% 
  left_join(tracker_data_raw %>% select(Name, `Student ID`), by = "Name")


noms <- peer_noms_raw %>% 
  group_by(Name, Trait, group_peer) %>% 
  summarise(`N peer nominations` = n(),
            `Student ID` = first(`Student ID`)) %>% 
  arrange(group_peer, Trait, `N peer nominations`)


ground_truth <- teacher_ratings_long %>% 
  left_join(noms, by = c("Name", "Student ID", "Trait")) %>% 
  mutate(`N peer nominations` = ifelse(is.na(`N peer nominations`), 0, `N peer nominations`)) %>% 
  group_by(group) %>% 
  mutate(scaled_nominations = scale(`N peer nominations`)) %>% 
  left_join(self_ratings_long %>% select(`Student ID`, Trait, Name, scaled_score) %>% rename(`Self-score` = scaled_score), by = c("Name", "Student ID", "Trait", "group_peer"))


ground_truth %>% 
  filter(!Trait %in% c("Interview-ability", "Creativity")) %>% 
  ggplot(aes(x = `Teacher Score`, y = scaled_nominations, colour = group)) +
  facet_wrap(~Trait + group) +
  geom_smooth(method = "lm") +
  geom_point() +
  labs(y = "Peer nominator score") +
  geom_abline(aes(intercept = 0, slope = 1))


ground_truth %>% 
  filter(!Trait %in% c("Interview-ability", "Creativity")) %>% 
  ggplot(aes(x = `Teacher Score`, y = `Self-score`, colour = group)) +
  facet_wrap(group~Trait ) +
  geom_smooth(method = "lm") +
  geom_point() +
  labs(y = "Self-score") +
  lims(y = c(-3, 3)) +
  geom_abline(aes(intercept = 0, slope = 1))

ground_truth %>% 
  filter(!Trait %in% c("Interview-ability", "Creativity")) %>% 
  ggplot(aes(x = scaled_nominations + `Teacher Score`, y = `Self-score`, colour = group)) +
  facet_wrap(~Trait + group) +
  geom_smooth(method = "lm") +
  geom_point() +
  labs(y = "Self-score", x = "Peer scores") +
  lims(y = c(-3, 3)) +
  geom_abline(aes(intercept = 0, slope = 1))

ground_truth %>% 
  filter(!Trait %in% c("Interview-ability", "Creativity")) %>%
  left_join(rmet_responses_long, by = "Student ID") %>% 
  group_by(group) %>% 
  mutate(score = scale(score)) %>%
  ggplot(aes(x = `Teacher Score`, y = score))+facet_wrap(~Trait + group) +
  geom_smooth(method = "lm") +
  geom_point()+
  #lims(y = c(-3, 3)) +
  labs(y = "RMET score") +
  geom_abline(aes(intercept = 0, slope = 1))


ground_truth %>% 
  filter(!Trait %in% c("Interview-ability", "Creativity")) %>%
  left_join(rmet_responses_long, by = "Student ID") %>% 
  group_by(group) %>% 
  mutate(score = scale(score)) %>%
  ggplot(aes(x = `Teacher Score`, y = score))+facet_wrap(~Trait) +
  geom_smooth(method = "lm") +
  geom_point()+
  #lims(y = c(-3, 3)) +
  labs(y = "RMET score") +
  geom_abline(aes(intercept = 0, slope = 1))




```

Pipeline {.storyboard}
====


### Student Pipeline

```{r}
tracker_data %>% 
  gather(Step, Completed) %>% 
  group_by(Step) %>% 
  summarise(`Number completed` = sum(Completed)) %>% 
  ggplot(aes(x = Step, y = `Number completed`)) +
  geom_bar(stat = "identity", fill = "blue", alpha = 0.6) +
  ggthemes::theme_hc() +
  theme(axis.text.x = element_text(angle = 270))
```


### Teacher pipeline

```{r}

```


Intelligence {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Intelligence"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  group_by(group) %>%
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  ungroup %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  #theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% 
              rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
    mutate(n = ifelse(is.na(n), 0, n),
           `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`, group), by = "Candidate") %>%
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`, group) %>%
  group_by(group) %>% 
  mutate(`Interviewer Score` = scale(`Interviewer Score`)) %>%
  ungroup %>%
  select(-group) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  #theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr) ) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```

Perseverance {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Perseverance"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  theme(axis.text.y= element_blank()) +
  facet_grid(~`Evidence Type`) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```


Empathy {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Empathy"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```

Integrity {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Integrity"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```

Spike {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Spike"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```


Boost {.storyboard}
====

### Teacher and peer scores

```{r}
tr <- "Boost"
teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name)) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>%
  select(`Student`, `Teacher Score`, `Peer Score`) %>%
  gather(Type, Score, -Student) %>%
  group_by(Student) %>% 
  mutate(mean_score = mean(Score)) %>%
  ungroup %>% 
  mutate(Student = reorder(Student, mean_score)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  coord_flip() +
  geom_point() +
  theme(axis.text.y= element_blank()) +
  ggthemes::theme_hc() +
  labs(title = paste0("Teacher and peer scores of ", tr))

```

### Adding interviews

```{r}
review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  left_join(teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`), by = "Candidate") %>% 
  mutate(Student = reorder(Student, `Teacher Score` + `Peer Score`),
         score = scale(score)) %>% 
  rename(`Interviewer Score` = score) %>% 
  select(`Interviewer`, `Student`, `Interviewer Score`, `Teacher Score`, `Peer Score`) %>%
  filter(!is.na(`Teacher Score`)) %>%
  gather(Type, Score, -1:-2) %>% 
  mutate(`Evidence Type` = ifelse(Type == "Interviewer Score", "Interview", "Ground Truth")) %>%
  group_by(Type, Student) %>%
  filter(1:n()<=ifelse(Type=="Interviewer Score",n(), 1)) %>%
  ggplot(aes(x = Student, y = Score, colour = Type)) +
  geom_jitter(width = 0.1) + 
  coord_flip() +
  ggthemes::theme_hc() +
  facet_grid(~`Evidence Type`) +
  theme(axis.text.y= element_blank()) +
  labs(title = paste0("Teacher, peer and interviewer scores of ", tr)) 

```

### Comparing ground truth to interviews

```{r}
ground_truth <- teacher_ratings_long %>% 
  filter(Trait == tr) %>% 
  left_join(noms %>% rename(Student = Name), by = c("Student", "Trait", "Candidate")) %>% 
  mutate(n = ifelse(is.na(n), 0, n),
         `Peer Score` = scale(n)) %>% 
    select(Student, Candidate, `Peer Score`, `Teacher Score`)
  

review_data %>% 
  filter(Trait == tr) %>% 
  rename(Candidate = `Candidate's Student ID (This is SOMETIMES their email! check the excel sheet)`, Interviewer = `Interviewer Name (you, the interviewer)`) %>% 
  group_by(Candidate) %>%
  summarize(`Interview Score Average` = mean(score)) %>% 
  left_join(ground_truth, by  = "Candidate") %>%
  mutate(`Ground Truth Score` = scale(`Peer Score` + `Teacher Score`)) %>% 
  ggplot(aes(x = `Ground Truth Score`, y = `Interview Score Average`)) +
  geom_point() +
  ggthemes::theme_hc() +
  labs(title = paste0("Ground truth vs interviews in ", tr))

```
